---
title: "lle-assignment4-improved"
author: "Laura Le"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(plotly)

```

#Question of Interest
Our current sales contest rewards successful emails, successful calls and client meetings. Meetings are always the goal, and they are achieved through successful emails and calls.   I'm wondering if successful emails and/or calls lead to more client meetings.

This data includes AVP Successful Activities for 8 weeks, from February - March 2019.  I collected this data from many different reports in Salesforce.  When completing Assignment 2, I reshaped the data and made it more useful for analysis.  I then anonymized the data for the purpose of this assignment.

#Answer
There appears to be a positive correlation between Successful Emails and Meetings.  Interestingly, only AVP's with more than average Successful Emails had more than Average Meetings.  Also, more than Average Successful Emails does not guarentee more than Average Successful Calls.  For further analysis, I recommend looking at the type of emails that are being sent.  I would expect more emails to be exchanged as a sale comes to a close.  I'm interested in knowing how many true prospecting emails (ie. email blasts, phone call follow-up), and the impact they have on scheduling meetings with new businesses.

```{r data}

mydata <- read.csv("AVPTotalsAnonymous.csv")
head(mydata)
summary(mydata)

mydata <- mydata %>%mutate(
  ID = as.character(ID))

plot_ly(data=mydata, x = ~CallTotal, y = ~MeetingTotal)
plot_ly(data=mydata, x = ~EmailTotal, y = ~MeetingTotal)

#comparing Email Totals to Meeting Totals proves to be a more interesting graph

```
```{r}

library(broom)

plot_ly(data=mydata, x = ~EmailTotal, y = ~MeetingTotal,
        text = ~paste0("ID#  ", ID), name = 'AVP')%>%
  add_trace(p=., type = "scatter")%>%
  add_segments(x = 80, xend = 80, yend = 0, name = 'Average number of Successful Emails') %>%
  add_segments(x = 0, xend = 600, y = 15, yend = 15, name = 'Average number Meetings') %>%
  layout(xaxis = list(title = "Number of Successful Emails"),
         yaxis = list(title = "Number Meetings"),
         title = "Positive correlation between Successful Emails and Meetings")

```

